A formal treatment of bidirectional typing\texorpdfstring{\thanks{The work is supported by the National Science and Technology Council of Taiwan under grant NSTC 112-2221-E-001-003-MY3.}}{}

### 2024-01-05 tex/ESOP24/S8-future.tex
[ tex ] Add the citation for Ahrens et al.'s work

For the second group, theories developed in set theory can often be reformulated in type theory and thus manageable for formalisation in a type-theoretic proof assistant. 
Such examples include frameworks developed by \citet{Allais2021,Fiore2022} in \Agda, which are relatively correct to their meta-language, although their expressiveness is limited to simply typed theories.
Our work belongs to the second group, as we aim for a formalism in a constructive type theory to minimise the gap between theory and implementation.

>>>>

For the second group, theories developed in set theory can often be reformulated in type theory and thus manageable for formalisation in a type-theoretic proof assistant. 
Such examples include frameworks developed by \citet{Allais2021,Ahrens2022,Fiore2022} in \Agda, which are relatively correct to their meta-language, although their expressiveness is limited to simply typed theories.
Our work belongs to the second group, as we aim for a formalism in a type theory to minimise the gap between theory and implementation.
